
---
title: "`r params$countrynamet`"
output:
   pdf_document: default
   latex_engine: pdflatex
   fig_caption: yes
   keep_tex: yes
   urlcolor: blue
fontsize: 9pt
geometry: "left=1.3cm,right=1.3cm,top=1.5cm,bottom=2.1cm"
header-includes:  \usepackage{fancyhdr} 
  \usepackage{graphicx}
  \usepackage{eurosym}
  \usepackage{datetime}
  \usepackage{booktabs,xcolor} \pagestyle{fancy}  
  \fancypagestyle{plain}{\pagestyle{fancy}}
  \pagenumbering{gobble}
  \renewcommand\thefootnote{\textcolor{black}{\arabic{footnote}}}
  \usepackage{pagecolor}
  \pagecolor{white}
  \usepackage{fourier}
  \usepackage[fontsize=8.7pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{xcolor}
  \usepackage{multicol}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
  \usepackage{caption}
  \captionsetup{skip=0pt}
  \usepackage{hyperref}
  \usepackage{array}
  \usepackage{varwidth}
  \hypersetup{
      colorlinks=true,
      linkcolor=blue,
      filecolor=magenta,      
      urlcolor=cyan,
  }
  \urlstyle{same}
  \usepackage{enumitem}
  \setlist{leftmargin=*}
  \pagenumbering{gobble}
  \usepackage{numprint}
  \usepackage{fbox}
  
params:
  countrynamet: "Afghanistan"   

---
\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\definecolor{steelblue}{rgb}{0.27, 0.51, 0.71}
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
\newcommand\boldblue[1]{\textcolor{bondiblue}{\textbf{#1}}}

This 2-page brief provides the 2020 Human Capital Index (HCI) released in September 2020, and a set of indicators that are complementary to the HCI. The HCI measures the amount of human capital that a child born today can expect to attain by age 18. It conveys the productivity of the next generation of workers compared to a benchmark of complete education and full health. Although the effects of COVID-19 on the HCI are yet to be measured due to the lack of data, we expect the post-pandemic HCI to be relatively lower due to the deep learning and health losses globally. **Data collection efforts to allow updates to the HCI remain critical for all countries to inform policies and programs to address the setbacks to human capital.**

\Begin{multicols}{2}

### \boldblue{T\small{HE HUMAN CAPITAL INDEX}}###

`r x[which(x$wbcountryname == params$countrynamet),"hci_text_1"]` 

`r x[which(x$wbcountryname == params$countrynamet),"hci_text_2"]` 

### \boldblue{T\small{HE HUMAN CAPITAL INDEX COMPONENTS}}###

* **Probability of Survival to Age 5.** `r x[which(x$wbcountryname == params$countrynamet),"psurv_mf_2020_text"]`

* **Expected Years of School.** `r x[which(x$wbcountryname == params$countrynamet),"eyrs_mf_2020_text"]`

* **Harmonized Test Scores.** `r x[which(x$wbcountryname == params$countrynamet),"test_mf_2020_text"]`

* **Learning-adjusted Years of School.** `r x[which(x$wbcountryname == params$countrynamet),"qeyrs_mf_2020_text"]`

* **Adult Survival Rate.** `r x[which(x$wbcountryname == params$countrynamet),"asr_mf_2020_text"]`

* **Fraction of Children Under 5 Not Stunted.** `r x[which(x$wbcountryname == params$countrynamet),"nostu_mf_2020_text"]`

### \boldblue{D\small{IFFERENCES IN HCI ACROSS GENDER AND SOCIO-ECONOMIC GROUPS}}###

`r x[which(x$wbcountryname == params$countrynamet),"gender_text_1"]` `r x[which(x$wbcountryname == params$countrynamet),"ses_hci_text_1"]`

\vspace{-1mm}
\begin{table}[H]
\renewcommand{\tabcolsep}{0.8mm}
\begin{tabular}{lcccccccccccccccc}
\\\textbf{     }   &    & & & & & & & & & & & & & &             &  \\ \hline
                         &      & & & & & & & & & & & & & &              & \\
\textbf{ HCI and its components   } & & & & & & & & & & & & & & \textbf{ Boys} & \textbf{ Girls} &  \textbf{ Overall} \\\hline
\vspace{-1mm} \\
HCI & & & & & & & & & & & & & &   `r x[which(x$wbcountryname == params$countrynamet),"hci_m_2020_t"]` &   `r x[which(x$wbcountryname == params$countrynamet),"hci_f_2020_t"]` &    `r x[which(x$wbcountryname == params$countrynamet),"hci_mf_2020_t"]`\\
Survival to Age 5 & & & & & & & & & & & & & & `r x[which(x$wbcountryname == params$countrynamet),"psurv_m_2020_t"]`  &  `r x[which(x$wbcountryname == params$countrynamet),"psurv_f_2020_t"]` & `r x[which(x$wbcountryname == params$countrynamet),"psurv_mf_2020_t"]` \\
Expected Years of School & & & & & & & & & & & & & &  `r x[which(x$wbcountryname == params$countrynamet),"eyrs_m_2020_t"]`   &  `r x[which(x$wbcountryname == params$countrynamet),"eyrs_f_2020_t"]`  &  `r x[which(x$wbcountryname == params$countrynamet),"eyrs_mf_2020_t"]` \\
Harmonized Test Scores & & & & & & & & & & & & & &  `r x[which(x$wbcountryname == params$countrynamet),"test_m_2020_t"]` &  `r x[which(x$wbcountryname == params$countrynamet),"test_f_2020_t"]` & `r x[which(x$wbcountryname == params$countrynamet),"test_mf_2020_t"]` \\
Learning-adjusted Years of School & & & & & & & & & & & & & &  `r x[which(x$wbcountryname == params$countrynamet),"qeyrs_m_2020_t"]`  &  `r x[which(x$wbcountryname == params$countrynamet),"qeyrs_f_2020_t"]`  &  `r x[which(x$wbcountryname == params$countrynamet),"qeyrs_mf_2020_t"]`\\
Adult Survival Rate & & & & & & & & & & & & & & `r x[which(x$wbcountryname == params$countrynamet),"asr_m_2020_t"]`  &  `r x[which(x$wbcountryname == params$countrynamet),"asr_f_2020_t"]`  &  `r x[which(x$wbcountryname == params$countrynamet),"asr_mf_2020_t"]`\\
Not Stunted Rate & & & & & & & & & & & & & & `r x[which(x$wbcountryname == params$countrynamet),"nostu_m_2020_t"]`  & `r x[which(x$wbcountryname == params$countrynamet),"nostu_f_2020_t"]`  &  `r x[which(x$wbcountryname == params$countrynamet),"nostu_mf_2020_t"]`\\
                         & & & & & & & & & & & & & & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &    
\vspace{-4mm}
\\\hline
\end{tabular}
\vspace{1mm} 
\end{table}


```{r gr2, out.height= "80%", fig.align = "right", echo=FALSE}
gr2 <- paste0("p1/p1_", x[which(x$wbcountryname == params$countrynamet),"wbcode"],"_all.pdf")
knitr::include_graphics(gr2)
```

\vfill

\End{multicols}


\newpage

\vspace{3mm} 

Human capital, a crucial ingredient for economic growth, is multi-dimensional and cumulatively built over the lifecycle. `r x[which(x$wbcountryname == params$countrynamet),"hcci_text"]` These selected HCCIs are based on the latest available data (\emph{italicized} and shown in parenthesis) and benchmarked against regional and country income group averages. **They highlight where the need is for investment in people in each stage of life and for data collection and updates for evidence-based policy making.**

\vspace{1mm}

\Begin{multicols}{2}

### \boldblue{E\small{ARLY CHILDHOOD}}###

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_early_1"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_early_1"]`

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_early_2"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_early_2"]`

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_early_3"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_early_3"]`


### \boldblue{S\small{CHOOL AGE}}###

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_school_1"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_school_1"]`

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_school_2"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_school_2"]`

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_school_3"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_school_3"]`

### \boldblue{Y\small{OUTH}}###

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_youth_1"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_youth_1"]`

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_youth_2"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_youth_2"]`

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_youth_3"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_youth_3"]`

### \boldblue{A\small{DULTS \& ELDERLY}}###

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_adults_1"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_adults_1"]`

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_adults_2"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_adults_2"]`

* **`r x[which(x$wbcountryname == params$countrynamet),"lab_adults_3"]`.** `r x[which(x$wbcountryname == params$countrynamet),"text_adults_3"]`


```{r gr3, out.height= "88%", fig.align = "right", echo=FALSE}
gr3 <- paste0("p2/p2_", x[which(x$wbcountryname == params$countrynamet),"wbcode"], "_stages.pdf")
knitr::include_graphics(gr3)
```

\End{multicols}
