

---
title: "`r params$countrynamet``r params$extra`"
output:
  pdf_document: 
    keep_tex: true
  latex_engine: pdflatex
  fig_caption: yes
  urlcolor: blue
fontsize: 9pt
geometry: "left=1.3cm,right=1.3cm,top=1.5cm,bottom=0.5cm"
header-includes:  \usepackage{fancyhdr} 
  \usepackage{graphicx}
  \usepackage{eurosym}
  \usepackage{datetime}
  \usepackage{booktabs,xcolor} \pagestyle{fancy}  
  \fancypagestyle{plain}{\pagestyle{fancy}}
  \pagenumbering{gobble}
  \renewcommand\thefootnote{\textcolor{black}{\arabic{footnote}}}
  \usepackage{pagecolor}
  \pagecolor{white}
  \usepackage{fourier}
  \usepackage[fontsize=8.7pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{xcolor}
  \usepackage{multicol}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
  \usepackage{caption}
  \captionsetup{skip=0pt}
  \usepackage{hyperref}
  \usepackage{array}
  \usepackage{varwidth}
  \hypersetup{
      colorlinks=true,
      linkcolor=blue,
      filecolor=magenta,      
      urlcolor=cyan,
  }
  \urlstyle{same}
  \usepackage{enumitem}
  \setlist{leftmargin=*}
  \pagenumbering{gobble}
  \usepackage{numprint}
  \usepackage{fbox}
  
params:
  countrynamet: "Afghanistan"
  extra: ""

---
\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\definecolor{steelblue}{rgb}{0.27, 0.51, 0.71}
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
\newcommand\boldblue[1]{\textcolor{bondiblue}{\textbf{#1}}}

This two-page brief provides the 2020 Human Capital Index (HCI) released in September 2020, and a set of complementary indicators. The HCI measures the potential amount of human capital that a child born today can attain by age 18, conveying the productivity of the next generation of workers compared to a benchmark of complete education and full health. While the effects of COVID-19 on this index are yet to be measured due to the lack of data, we expect the post-pandemic HCI to be relatively lower due to significant global setbacks in deep learning and health. **Data collection efforts to allow updates to the HCI remain critical for all countries to inform policies and programs to address the setbacks to human capital.**

\Begin{multicols}{2}

### \boldblue{T\small{HE HUMAN CAPITAL INDEX}}###

`r x[which(x$wbcountryname == params$countrynamet),"hci_text_1"]` 

`r x[which(x$wbcountryname == params$countrynamet),"hci_text_2"]` 

### \boldblue{T\small{HE HUMAN CAPITAL INDEX COMPONENTS}}###

* **Probability of Survival to Age 5.** `r x[which(x$wbcountryname == params$countrynamet),"psurv_text"]`

* **Expected Years of School.** `r x[which(x$wbcountryname == params$countrynamet),"eyrs_text"]`

* **Harmonized Test Scores.** `r x[which(x$wbcountryname == params$countrynamet),"test_text"]`

* **Learning-adjusted Years of School.** `r x[which(x$wbcountryname == params$countrynamet),"qeyrs_text"]`

* **Adult Survival Rate.** `r x[which(x$wbcountryname == params$countrynamet),"asr_text"]`

* **Fraction of Children Under 5 Not Stunted.** `r x[which(x$wbcountryname == params$countrynamet),"nostu_text"]`


<<<<<<< Updated upstream
<<<<<<< Updated upstream
### \boldblue{U\small{TILIZATION-ADJUSTED HUMAN CAPITAL}}###
=======
Only **`r round(( 1-x[which(x$wbcountryname == params$countrynamet), "not_employed"])*100)` percent** of working-age people in `r params$countrynamet` are employed. This results in a decreasing productivity by an additional  **`r round(100*x[which(x$wbcountryname == params$countrynamet), "not_employed"])` percent**. Thus, **a child born today is only `r round(x[which(x$wbcountryname == params$countrynamet), "uhci"])` percent as productive** as they could be if they had access to proper health, education, and their future labor was fully utilized in employment.
>>>>>>> Stashed changes

As the returns on human capital materialize through work, we introduce a utilization-adjusted Human Capital Index (UHCI) that adjust the HCI for underutilization, by taking into account the proportion of the employed working-age population. 
=======
`r x[which(x$wbcountryname == params$countrynamet), "uhci_text"]`

>>>>>>> Stashed changes

* In `r params$countrynamet`, adjusting the HCI for utilization leads to a decrease to `r round(x[which(x$wbcountryname == params$countrynamet), "uhci"])` percent. This suggests that nearly `r x[which(x$wbcountryname == params$countrynamet),"compare_uhci"]` of `r params$countrynamet`'s population is unable to fully leverage their skills and knowledge to contribute effectively to the economy.

* Comparing by gender, the utilization-adjusted of human capital is `r x[which(x$wbcountryname == params$countrynamet),"comparegender_uhci"]` for males (`r round(x[which(x$wbcountryname == params$countrynamet), "uhci_m"])` percent) than for females (`r round(x[which(x$wbcountryname == params$countrynamet), "uhci_f"])` percent)

\vspace{-0.5mm}
\begin{table}[H]
\renewcommand{\tabcolsep}{0.8mm}
\begin{tabular}{m{0.3\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}}
\\\textbf{     }   &    &             &  \\ \hline
                         &      &              & \\
\textbf{ Human Capital and Utilization   } & \textbf{ Boys} & \textbf{ Girls} &  \textbf{ Overall} \\\hline
\vspace{-1mm} \\
Human Capital Index (HCI) &   `r x[which(x$wbcountryname == params$countrynamet),"hci_m_table_t"]` &   `r x[which(x$wbcountryname == params$countrynamet),"hci_f_table_t"]` &    `r x[which(x$wbcountryname == params$countrynamet),"hci_table_t"]`\\
Utilization-Adjusted Human Capital Index (UHCI) & `r x[which(x$wbcountryname == params$countrynamet),"uhci_m_table_t"]`  &  `r x[which(x$wbcountryname == params$countrynamet),"uhci_f_table_t"]` & `r x[which(x$wbcountryname == params$countrynamet),"uhci_table_t"]` \\
                         & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &    
\vspace{-4mm}
\\\hline
\end{tabular}
\vspace{1mm} 
\end{table}

```{r gr2, out.height= "80%", fig.align = "right", echo=FALSE}
gr2 <- paste0("Graph no subt/p1_", x[which(x$wbcountryname == params$countrynamet),"wbcode"],"_all", params$extra,".jpg")
knitr::include_graphics(gr2)
```

\vfill

\End{multicols}


\newpage

\vspace{3mm} 

Human capital, a crucial ingredient for economic growth, is multi-dimensional and cumulatively built over the lifecycle. `r x[which(x$wbcountryname == params$countrynamet),"hcci_text"]` These selected HCCIs are based on the latest available data (\emph{italicized} and shown in parentheses) and benchmarked against regional and country income group averages. **They highlight where there is need for investment in people in each stage of life and for data collection and updates for evidence-based policy making.**

\vspace{1mm}

\Begin{multicols}{2}

### \boldblue{E\small{ARLY CHILDHOOD}}###

* `r x[which(x$wbcountryname == params$countrynamet),"l1_text"]`

* `r x[which(x$wbcountryname == params$countrynamet),"l2_text"]`

* `r x[which(x$wbcountryname == params$countrynamet),"l3_text"]`


### \boldblue{S\small{CHOOL AGE}}###

* `r x[which(x$wbcountryname == params$countrynamet),"e1_text"]`

* `r x[which(x$wbcountryname == params$countrynamet),"e2_text"]`

* `r x[which(x$wbcountryname == params$countrynamet),"e3_text"]`

### \boldblue{Y\small{OUTH}}###

* `r x[which(x$wbcountryname == params$countrynamet),"h1_text"]`

* `r x[which(x$wbcountryname == params$countrynamet),"h2_text"]`

* `r x[which(x$wbcountryname == params$countrynamet),"h3_text"]`

### \boldblue{A\small{DULTS \& ELDERLY}}###

* `r x[which(x$wbcountryname == params$countrynamet),"b1_text"]`

* `r x[which(x$wbcountryname == params$countrynamet),"b2_text"]`

* `r x[which(x$wbcountryname == params$countrynamet),"b3_text"]`


```{r gr3, out.height= "88%", fig.align = "right", echo=FALSE}
gr3 <- paste0("Graph no subt/p2_", x[which(x$wbcountryname == params$countrynamet),"wbcode"], "_stages", params$extra,".jpg")
knitr::include_graphics(gr3)
```

\End{multicols}