

---
title: "`r params$countrynamet``r params$extra`"
output:
  pdf_document: 
    keep_tex: true
  latex_engine: pdflatex
  fig_caption: yes
  urlcolor: blue
fontsize: 9pt
geometry: "left=1.3cm,right=1.3cm,top=1.5cm,bottom=0.5cm"
header-includes:  \usepackage{fancyhdr} 
  \usepackage{graphicx}
  \usepackage{eurosym}
  \usepackage{datetime}
  \usepackage{booktabs,xcolor} \pagestyle{fancy}  
  \fancypagestyle{plain}{\pagestyle{fancy}}
  \pagenumbering{gobble}
  \renewcommand\thefootnote{\textcolor{black}{\arabic{footnote}}}
  \usepackage{pagecolor}
  \pagecolor{white}
  \usepackage{fourier}
  \usepackage[fontsize=9.1pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{xcolor}
  \usepackage{multicol}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
  \usepackage{caption}
  \captionsetup{skip=0pt}
  \usepackage{hyperref}
  \usepackage{array}
  \usepackage{varwidth}
  \hypersetup{
      colorlinks=true,
      linkcolor=blue,
      filecolor=magenta,      
      urlcolor=cyan,
  }
  \urlstyle{same}
  \usepackage{enumitem}
  \setlist{leftmargin=*}
  \pagenumbering{gobble}
  \usepackage{numprint}
  \usepackage{fbox}
  \renewcommand{\tightlist}{\setlength{\itemsep}{1ex}\setlength{\parskip}{0pt}}
  
params:
  countrynamet: "Afghanistan"
  extra: ""

---
\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\definecolor{steelblue}{rgb}{0.27, 0.51, 0.71}
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
\newcommand\boldblue[1]{\textcolor{bondiblue}{\textbf{#1}}}

\vspace{1em}

`r x[which(x$wbcountryname == params$countrynamet),"first_par"]` This page presents the Human Capital Index (HCI), its components parts, and relevant benchmarks. The HCI quantifies how underinvestment in education and health for today’s children reduces future incomes. Data are the most recently available as of 2020. The back page presents a set of Human Capital Complementary Indicators (HCCI) that shows progress at each stage of the lifecycle.

\vspace{0.5em}

\Begin{multicols}{2}  

\raggedcolumns

\vspace{-2mm}
### \boldblue{T\small{HE HUMAN CAPITAL INDEX}}###
\vspace{-2mm}

`r x[which(x$wbcountryname == params$countrynamet),"hci_text_1"]` 

`r x[which(x$wbcountryname == params$countrynamet),"hci_text_2"]` 

\vspace{-2mm}
### \boldblue{T\small{HE HUMAN CAPITAL INDEX COMPONENTS}}###
\vspace{-2mm}

* **Probability of Survival to Age 5.** `r x[which(x$wbcountryname == params$countrynamet),"psurv_text"]`

* **Expected Years of School.** `r x[which(x$wbcountryname == params$countrynamet),"eyrs_text"]`

* **Learning-Adjusted Years of School.** `r x[which(x$wbcountryname == params$countrynamet),"qeyrs_text"]`

* **Average Harmonized Test Scores.** `r x[which(x$wbcountryname == params$countrynamet),"test_text"]`

* **Adult Survival Rate.** `r x[which(x$wbcountryname == params$countrynamet),"asr_text"]`

* **Fraction of Children Under 5 Not Stunted.** `r x[which(x$wbcountryname == params$countrynamet),"nostu_text"]`

\vspace{-6mm}
### \boldblue{U\small{TILIZATION-ADJUSTED HUMAN CAPITAL INDEX}}###
\vspace{-2mm}

`r x[which(x$wbcountryname == params$countrynamet), "uhci_text"]`

<!-- \vspace{-2mm} -->
\begin{table}[H]
\renewcommand{\tabcolsep}{0.8mm}
\begin{tabular}{m{0.29\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}}

 \multicolumn{4}{c}{\bf{Gender differences in Human Capital and Utilization}} \\\hline
 \vspace{-1mm}   \\
 & \textbf{Boys} & \textbf{Girls} &  \textbf{Overall} \\\hline
\vspace{-1mm} \\
Human Capital Index &   `r x[which(x$wbcountryname == params$countrynamet),"hci_m_t"]` &   `r x[which(x$wbcountryname == params$countrynamet),"hci_f_t"]` &    `r x[which(x$wbcountryname == params$countrynamet),"hci_t"]` \\
Utilization-Adjusted HCI & `r x[which(x$wbcountryname == params$countrynamet),"uhci_m_t"]`  &  `r x[which(x$wbcountryname == params$countrynamet),"uhci_f_t"]` & `r x[which(x$wbcountryname == params$countrynamet),"uhci_t"]` \\
                         & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &    
\vspace{-4mm}
\\\hline
\multicolumn{4}{l}{\small{Note:} - \small{represents no internationally comparable data available.}} \\
\end{tabular}
\vspace{1mm} 
\end{table}

\columnbreak

```{r gr2, out.height= "69%", fig.align = "right", echo=FALSE}
gr2 <- paste0("Graphs/p1_", x[which(x$wbcountryname == params$countrynamet),"wbcode"],"_all", params$extra,".jpg")
knitr::include_graphics(gr2)
```

\vspace{-5mm}
\small Note: Missing symbols indicate internationally comparable data are not available to generate the corresponding indicator.


\End{multicols}


\newpage
 
$$\\[-3em]$$

**The Human Capital Complementary Indicators (HCCIs) offer a snapshot of human capital investments at four stages of the lifecycle.** The figures show the latest available data, benchmarked against regional averages. The figures also report progress over the previous 5 years.

\vspace{1mm}

\Begin{multicols}{2} 

\raggedcolumns

### \boldblue{E\small{ARLY CHILDHOOD}}###

* `r x[which(x$wbcountryname == params$countrynamet),"l1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"l2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"l3_text"]`

### \boldblue{S\small{CHOOL AGE}}###

* `r x[which(x$wbcountryname == params$countrynamet),"e1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"e2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"e3_text"]`

### \boldblue{Y\small{OUTH}}###

* `r x[which(x$wbcountryname == params$countrynamet),"h1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"h2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"h3_text"]`

### \boldblue{A\small{DULTS \& ELDERLY}}###

* `r x[which(x$wbcountryname == params$countrynamet),"b1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"b2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"b3_text"]`

\columnbreak 

```{r gr3, out.height= "86%", fig.align = "right", echo=FALSE}
gr3 <- paste0("Graphs/p2_", x[which(x$wbcountryname == params$countrynamet),"wbcode"], "_stages", params$extra,".jpg")
knitr::include_graphics(gr3)
```

\vspace{-5mm}
\small Note: Missing symbols indicate internationally comparable data are not available to generate the corresponding indicator.

<!-- \vspace(0.1mm) -->

\End{multicols}