

---
title: "`r params$countrynamet``r params$extra`"
output:
  pdf_document: 
    keep_tex: true
  latex_engine: pdflatex
  fig_caption: yes
  urlcolor: blue
fontsize: 9pt
geometry: "left=1.3cm,right=1.3cm,top=1.5cm,bottom=0.5cm"
header-includes:  \usepackage{fancyhdr} 
  \usepackage{graphicx}
  \usepackage{eurosym}
  \usepackage{datetime}
  \usepackage{booktabs,xcolor} \pagestyle{fancy}  
  \fancypagestyle{plain}{\pagestyle{fancy}}
  \pagenumbering{gobble}
  \renewcommand\thefootnote{\textcolor{black}{\arabic{footnote}}}
  \usepackage{pagecolor}
  \pagecolor{white}
  \usepackage{fourier}
  \usepackage[fontsize=8.7pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{xcolor}
  \usepackage{multicol}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
  \usepackage{caption}
  \captionsetup{skip=0pt}
  \usepackage{hyperref}
  \usepackage{array}
  \usepackage{varwidth}
  \hypersetup{
      colorlinks=true,
      linkcolor=blue,
      filecolor=magenta,      
      urlcolor=cyan,
  }
  \urlstyle{same}
  \usepackage{enumitem}
  \setlist{leftmargin=*}
  \pagenumbering{gobble}
  \usepackage{numprint}
  \usepackage{fbox}
  \renewcommand{\tightlist}{\setlength{\itemsep}{1ex}\setlength{\parskip}{0pt}}
  
params:
  countrynamet: "Afghanistan"
  extra: ""

---
\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\definecolor{steelblue}{rgb}{0.27, 0.51, 0.71}
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
\newcommand\boldblue[1]{\textcolor{bondiblue}{\textbf{#1}}}

\vspace{2.3em}

**Human capital – knowledge, skills, and good health – empowers people to achieve their potential and drives economic growth. This brief tracks progress by `r params$countrynamet` in building and using human capital.** Page 1 presents the Human Capital Index (HCI), its components parts, and relevant country benchmarks. The HCI quantifies how underinvestment in education and health for today’s children reduces future incomes. The data are from 2020. Page 2 presents a set of Human Capital Complementary Indicators (HCCI) that show progress at each stage of the lifecycle.


\vspace{0.5em}

\Begin{multicols}{2}

\vspace{-2mm}
### \boldblue{T\small{HE HUMAN CAPITAL INDEX}}###
\vspace{-2mm}

`r x[which(x$wbcountryname == params$countrynamet),"hci_text_1"]` 

`r x[which(x$wbcountryname == params$countrynamet),"hci_text_2"]` 

\vspace{-2mm}
### \boldblue{T\small{HE HUMAN CAPITAL INDEX COMPONENTS}}###
\vspace{-2mm}

* **Proportion of live births that will survive until age 5.** `r x[which(x$wbcountryname == params$countrynamet),"psurv_text"]`

* **Expected Years of School.** `r x[which(x$wbcountryname == params$countrynamet),"eyrs_text"]`

* **Average Harmonized Test Scores.** `r x[which(x$wbcountryname == params$countrynamet),"test_text"]`

* **Learning-Adjusted Years of School.** `r x[which(x$wbcountryname == params$countrynamet),"qeyrs_text"]`

* **Proportion of 15-year-olds that will survive until age 60.** `r x[which(x$wbcountryname == params$countrynamet),"asr_text"]`

* **Proportion of Children Under 5 Not Stunted.** `r x[which(x$wbcountryname == params$countrynamet),"nostu_text"]`

\vspace{-6mm}
### \boldblue{U\small{TILIZATION-ADJUSTED HUMAN CAPITAL INDEX}}###
\vspace{-2mm}

`r x[which(x$wbcountryname == params$countrynamet), "uhci_text"]`


\vspace{-7mm}
\begin{table}[H]
\renewcommand{\tabcolsep}{0.8mm}
\begin{tabular}{m{0.29\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}}
\\\textbf{     }   &    &             &  \\ \hline
                         &      &              & \\
\textbf{ Human Capital and Utilization   } & \textbf{Boys} & \textbf{Girls} &  \textbf{Overall} \\\hline
\vspace{-1mm} \\
Human Capital Index &   `r x[which(x$wbcountryname == params$countrynamet),"hci_m_t"]` &   `r x[which(x$wbcountryname == params$countrynamet),"hci_f_t"]` &    `r x[which(x$wbcountryname == params$countrynamet),"hci_t"]` \\
Utilization-Adjusted Human Capital Index & `r x[which(x$wbcountryname == params$countrynamet),"uhci_m_t"]`  &  `r x[which(x$wbcountryname == params$countrynamet),"uhci_f_t"]` & `r x[which(x$wbcountryname == params$countrynamet),"uhci_t"]` \\
                         & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &    
\vspace{-4mm}
\\\hline
\end{tabular}
\vspace{1mm} 
\end{table}

```{r gr2, out.height= "80%", fig.align = "right", echo=FALSE}
gr2 <- paste0("Graphs/p1_", x[which(x$wbcountryname == params$countrynamet),"wbcode"],"_all", params$extra,".jpg")
knitr::include_graphics(gr2)
```

\vfill

\End{multicols}


\newpage
 
$$\\[-3em]$$

**The Human Capital Complementary Indicators (HCCIs) offer a snapshot of human capital investments at four stages of the lifecycle.** The figures show the latest available data and progress over the last 5 years. The HCCIs are benchmarked against regional averages.

\vspace{1mm}

\Begin{multicols}{2}

### \boldblue{E\small{ARLY CHILDHOOD}}###

* `r x[which(x$wbcountryname == params$countrynamet),"l1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"l2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"l3_text"]`

### \boldblue{S\small{CHOOL AGE}}###

* `r x[which(x$wbcountryname == params$countrynamet),"e1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"e2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"e3_text"]`

### \boldblue{Y\small{OUTH}}###

* `r x[which(x$wbcountryname == params$countrynamet),"h1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"h2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"h3_text"]`

### \boldblue{A\small{DULTS \& ELDERLY}}###

* `r x[which(x$wbcountryname == params$countrynamet),"b1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"b2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"b3_text"]`


```{r gr3, out.height= "82%", fig.align = "right", echo=FALSE}
gr3 <- paste0("Graphs/p2_", x[which(x$wbcountryname == params$countrynamet),"wbcode"], "_stages", params$extra,".jpg")
knitr::include_graphics(gr3)
```

\End{multicols}