

---
title: "`r params$countrynamet``r params$extra`"
output:
  pdf_document: 
    keep_tex: true
  latex_engine: pdflatex
  fig_caption: yes
  urlcolor: blue
fontsize: 9pt
geometry: "left=1.3cm,right=1.3cm,top=1.5cm,bottom=0.5cm"
header-includes:  \usepackage{fancyhdr} 
  \usepackage{graphicx}
  \usepackage{eurosym}
  \usepackage{datetime}
  \usepackage{booktabs,xcolor} \pagestyle{fancy}  
  \fancypagestyle{plain}{\pagestyle{fancy}}
  \pagenumbering{gobble}
  \renewcommand\thefootnote{\textcolor{black}{\arabic{footnote}}}
  \usepackage{pagecolor}
  \pagecolor{white}
  \usepackage{fourier}
  \usepackage[fontsize=8.7pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{xcolor}
  \usepackage{multicol}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
  \usepackage{caption}
  \captionsetup{skip=0pt}
  \usepackage{hyperref}
  \usepackage{array}
  \usepackage{varwidth}
  \hypersetup{
      colorlinks=true,
      linkcolor=blue,
      filecolor=magenta,      
      urlcolor=cyan,
  }
  \urlstyle{same}
  \usepackage{enumitem}
  \setlist{leftmargin=*}
  \pagenumbering{gobble}
  \usepackage{numprint}
  \usepackage{fbox}
  \renewcommand{\tightlist}{\setlength{\itemsep}{1ex}\setlength{\parskip}{0pt}}
  
params:
  countrynamet: "Afghanistan"
  extra: ""

---
\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\definecolor{steelblue}{rgb}{0.27, 0.51, 0.71}
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
\newcommand\boldblue[1]{\textcolor{bondiblue}{\textbf{#1}}}

\vspace{2.3em}

**Human capital –the knowledge, skills, and health that enable people to be productive members of society– is a critical ingredient for economic growth. This brief tracks `r params$countrynamet` progress in accumulating and using human capital through two sets of indicators.** Page 1 presents the Human Capital Index (HCI), its component parts, and relevant country benchmarks. The HCI measures the foregone productivity of the next generation of workers due to incomplete education and health investments in today's children.  The utilization-adjusted HCI takes into account additional foregone productivity of non-working adults. The data are from 2020. Page 2 presents Human Capital Complementary Indicators (HCCI) that proxy success at each stage of the lifecycle, based on the most recent data. 

\vspace{0.5em}

\Begin{multicols}{2}

\vspace{-2mm}
### \boldblue{T\small{HE HUMAN CAPITAL INDEX}}###
\vspace{-2mm}

`r x[which(x$wbcountryname == params$countrynamet),"hci_text_1"]` 

`r x[which(x$wbcountryname == params$countrynamet),"hci_text_2"]` 

\vspace{-2mm}
### \boldblue{T\small{HE HUMAN CAPITAL INDEX COMPONENTS}}###
\vspace{-2mm}

* **Fraction of live births that will survive until age 5.** `r x[which(x$wbcountryname == params$countrynamet),"psurv_text"]`

* **Expected Years of School.** `r x[which(x$wbcountryname == params$countrynamet),"eyrs_text"]`

* **Average Harmonized Test Scores.** `r x[which(x$wbcountryname == params$countrynamet),"test_text"]`

* **Learning-Adjusted Years of School.** `r x[which(x$wbcountryname == params$countrynamet),"qeyrs_text"]`

* **Fraction of 15-year-olds that will survive until age 60.** `r x[which(x$wbcountryname == params$countrynamet),"asr_text"]`

* **Fraction of Children Under 5 Not Stunted.** `r x[which(x$wbcountryname == params$countrynamet),"nostu_text"]`

\vspace{-6mm}
### \boldblue{U\small{TILIZATION-ADJUSTED HUMAN CAPITAL INDEX}}###
\vspace{-2mm}

Around **`r round(x[which(x$wbcountryname == params$countrynamet), "not_employed"]*100)` percent** of working-age people in `r params$countrynamet` are not employed. This means they cannot use their human capital to increase their productivity, resulting in a decreasing productivity by an additional **`r round(x[which(x$wbcountryname == params$countrynamet), "not_employed"]*100)` percent**. Thus, **a child born today is only `r round(x[which(x$wbcountryname == params$countrynamet), "uhci"]*100)` percent as productive** as they could be if they had access to proper health, education, and their future labor was fully utilized in employment.

Comparing by gender, the utilization-adjusted human capital is `r x[which(x$wbcountryname == params$countrynamet),"comparegender_uhci"]` for males (`r round(x[which(x$wbcountryname == params$countrynamet), "uhci_m"]*100)` percent) than for females (`r round(x[which(x$wbcountryname == params$countrynamet), "uhci_f"]*100)` percent).

\vspace{-7mm}
\begin{table}[H]
\renewcommand{\tabcolsep}{0.8mm}
\begin{tabular}{m{0.29\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}>{\centering\arraybackslash}m{0.054\textwidth}}
\\\textbf{     }   &    &             &  \\ \hline
                         &      &              & \\
\textbf{ Human Capital and Utilization   } & \textbf{Boys} & \textbf{Girls} &  \textbf{Overall} \\\hline
\vspace{-1mm} \\
Human Capital Index &   `r round(x[which(x$wbcountryname == params$countrynamet),"hci_m"], 2)` &   `r round(x[which(x$wbcountryname == params$countrynamet),"hci_f"], 2)` &    `r round(x[which(x$wbcountryname == params$countrynamet),"hci"], 2)` \\
Utilization-Adjusted Human Capital Index & `r round(x[which(x$wbcountryname == params$countrynamet),"uhci_m"], 2)`  &  `r round(x[which(x$wbcountryname == params$countrynamet),"uhci_f"], 2)` & `r round(x[which(x$wbcountryname == params$countrynamet),"uhci"], 2)` \\
                         & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &    
\vspace{-4mm}
\\\hline
\end{tabular}
\vspace{1mm} 
\end{table}

```{r gr2, out.height= "80%", fig.align = "right", echo=FALSE}
gr2 <- paste0("Graphs/p1_", x[which(x$wbcountryname == params$countrynamet),"wbcode"],"_all", params$extra,".jpg")
knitr::include_graphics(gr2)
```

\vfill

\End{multicols}


\newpage
 
$$\\[-3em]$$

Human capital is multi-dimensional and cumulatively built over the lifecycle. The Human Capital Complementary Indicators (HCCIs) offer a snapshot of human capital investments at four stages of the lifecycle. They draw from the latest available data (italicized and shown in parentheses) and data 5-years prior. The HCCIs are benchmarked against regional averages and progress in the last five years.

\vspace{1mm}

\Begin{multicols}{2}

### \boldblue{E\small{ARLY CHILDHOOD}}###

* `r x[which(x$wbcountryname == params$countrynamet),"l1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"l2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"l3_text"]`

### \boldblue{S\small{CHOOL AGE}}###

* `r x[which(x$wbcountryname == params$countrynamet),"e1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"e2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"e3_text"]`

### \boldblue{Y\small{OUTH}}###

* `r x[which(x$wbcountryname == params$countrynamet),"h1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"h2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"h3_text"]`

### \boldblue{A\small{DULTS \& ELDERLY}}###

* `r x[which(x$wbcountryname == params$countrynamet),"b1_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"b2_text"]`
* `r x[which(x$wbcountryname == params$countrynamet),"b3_text"]`


```{r gr3, out.height= "82%", fig.align = "right", echo=FALSE}
gr3 <- paste0("Graphs/p2_", x[which(x$wbcountryname == params$countrynamet),"wbcode"], "_stages", params$extra,".jpg")
knitr::include_graphics(gr3)
```

\End{multicols}